---
title: "Data Mining in R FS23: Version Control"
output: html_document
---
```{r eval=TRUE, echo=FALSE, include=FALSE}
install.packages("stargazer")
install.packages("here")
library(stargazer)
library(here)
```

# Class Exercise 1

## 1. Introduction
Satisfaction of the public with democracy is crucial for the functioning of
political ecosystems. We therefore investigate predictors for individuals'
satisfaction in Switzerland by having a look at the political interest and
media usage of the Swiss respondents from the European Social Survey. A 
regression analysis will then be conducted to assess the influence of some 
variables on satisfaction with democracy. Consequently, the research question
addressed here is:


- Does TV usage and political interest affect citizens' satisfaction with 
democracy?


With regards to the above question, following hypotheses have been elaborated 
which later will be tested using empirical data. 

1. Increased consumption of political contents on TV results in a lower 
satisfaction with democracy.
2. Higher political interest results in a lower satisfaction with democracy.

The confirmation of these hypotheses would show that low satisfaction with 
democracy can be a result of a high political literacy, rather than individuals
being not satisfied because they are not well informed about political affairs. 

## 2. Methods
Multiple regression analysis will be used as the dependent variable *stfdem* 
(satisfaction with democracy) is continuous. The variables of interest *tvpol*
(amount of political TV consumption) and *polintr* (political interest) are 
regarded as categorical data, thus for the analysis a reference category is built
in order to assess effects. By integrating also the variables *trstprl* (trust
in parliament), *gndr* (gender) and *agea* (age) into the model, we can control
for their effects. 

## 3. Results
Results in table 1 indicate that the chosen model as a whole does explain 
satisfaction with democracy only to a certain extent ($r^{2}$ = 0.257). It has also
to be stated that there is no significant influence of political TV consumption
on the dependent variable, meaning that H1 cannot be confirmed. On the other hand,
for H2 there is a significant result but not in favor of the hypothesis. 
The satisfaction of respondents stating they are "not at all interested" is
significantly lower than it is for very interested respondents. Both hypotheses 
with that have to be rejected.
```{r echo=FALSE, warning=FALSE, results='asis'}

dat <- readRDS(here("data", "data_processed.rds")) #load data

# modelling satisfaction with democracy
model_stfdem <- lm(stfdem ~ factor(tvpol) + factor(polintr) + trstprl + factor(gndr) 
            + agea, dat)
#summary(model_stfdem)

# show results in table
stargazer(model_stfdem, style = "ajps", 
          type = "html", title = "Table 1. Modelling Satisfaction with Democracy",
          out = here("data", "table.html"))
```


## 4. Discussion
What does the rejection of the hypotheses now mean for the research question? 
The regression analysis implies that there is an influence of the political
interest for individuals' satisfaction with democracy in Switzerland. But the
relation goes to an opposite direction as assumed in H2, meaning that highly
interested respondents are more satisfied with the state of democracy. On the
other hand, no evidence for TV usage showing an effect for satisfaction could
be found. Consequently, we conclude that satisfaction with democracy is shaped
more by personal interest for politics rather than by the consumption of
audiovisual contents. Future research should go further and investigate if media
usage affects political interest in order to assess possible interactions. 

